---
title: "Pre-Registration"
author: "Kathrin Reichmann"
date: "September 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Category Size and Generalization in EC 

Contains models of three previous tasks:
(1) Direct evaluative ratings
(2) AMP
(3) DRM

```{r prep, echo = FALSE, include = FALSE}
#set directory
knitr::opts_knit$set(root.dir = "C:/Users/siskr01/GitHub/CSCond_analysis/Study1_EC/data")
DRM <- "C:/Users/siskr01/GitHub/CSCond_analysis/Study2_DRM/data_preprocessed"


```


```{r, echo = FALSE, include = FALSE}
################### CS Variability: one-to-one vs. many-to-one
### july, 2021
### Kathrin Reichmann

### Plots and analysis for retreat

library(dplyr)
#library(tidyverse)
library(ggplot2)
library(lme4)
library(sjstats)
library(lmerTest)
library(afex)

#Functions
CI <- function(x) qnorm(0.975)*sd(x)/sqrt(length(x))
se <- function(x) sd(x)/sqrt(length(x))

### set working directory:
setwd("C:/Users/siskr01/GitHub/CSCond_analysis/Study1_EC/data")
DRM <- "C:/Users/siskr01/GitHub/CSCond_analysis/Study2_DRM/data_preprocessed"

# generalization: direct evaluative measure -------------------------------

#read table (pre-processed data)
direct <- read.csv2('direct.csv', header = TRUE)
str(direct)

as_factor <- c("subject", "val", "condition", "measure", "type", "type_specific", "category", "cs_selected")

for (factor in as_factor){
  direct[, factor] <- as.factor(direct[,factor])
}

direct$type_specific <- factor(direct$type_specific, levels = c("CS", "GS same", "GS different", "Feature", "Group"))

#delete variables we don't need
direct$X <- NULL
direct$type <- NULL

## randomly select 1 CS for many_one:
new_one <- direct[direct$condition == "one_one",]
new_many <- direct[direct$condition == "many_one",]

#remove the original CS evaluations
new_many <- new_many[!new_many$type_specific == "CS",]
new_direct <- rbind(new_one, new_many)

for (subject in unique(direct$subject)){
  if (direct$condition[direct$subject == subject] == "many_one"){
    for (cat in 1:4){
      temp <- direct[direct$subject == subject & direct$type_specific == "CS" & direct$category == cat,]
      select <- temp[1,]
      #concat only 1 CS rating per participant
      new_direct <- rbind(new_direct, select)
    }
  }
}
head(new_direct)

temp <- new_direct

# order data
temp <- temp[order(temp$subject, temp$val, temp$type_specific),]

# omit information we don't need
temp <- temp[!temp$type_specific =="GS different", ]
temp <- temp[!temp$type_specific == "Group",]
temp <- temp[!temp$type_specific == "Feature",]

## rename many_one to many and one_one to one
temp$condition <- factor(temp$condition, labels = c("one", "many"), levels = c("one_one", "many_one"))

##categorical variable: generalization as discrete
temp$type_specific <- factor(temp$type_specific, labels = c("CS", "GS"), levels = c("CS", "GS same"))

##### Data Analysis: Multilevel models (with valence)

### Effektkodierung -0.5, 0.5

#condition
temp$condition_effect <- 0
for (line in 1:dim(temp)[1]){
  if (temp$condition[line] == "one"){
    temp$condition_effect[line] <- -0.5
  } else {
    temp$condition_effect[line] <- 0.5
  }
}
temp$condition_effect

#valence
temp$val_effect <- 0
for (line in 1:dim(temp)[1]){
  if (temp$val[line] == "neg"){
    temp$val_effect[line] <- -0.5
  } else {
    temp$val_effect[line] <- 0.5
  }
}
temp$condition_effect
str(temp)

#type
temp$type_effect <- 0
for (line in 1:dim(temp)[1]){
  if (temp$type_specific[line] == "CS"){
    temp$type_effect[line] <- -0.5
  } else {
    temp$type_effect[line] <- 0.5
  }
}
temp$type_specific
str(temp)

#set default to dummy coding
options(contrasts = c("contr.treatment", "contr.poly"))
direct <- temp
direct <- direct[order(direct$subject, direct$val, direct$type_specific, direct$category),]

#analysis 1: difference scores
directNeg <- direct[direct$val == "neg",]
directPos <- direct$response[direct$val == "pos"]

directDiff <- cbind(directNeg, directPos)
directDiff$diff <- directDiff$directPos - directDiff$response
directDiff[directDiff$subject == "02a80kdxm7",]


#set default to dummy coding
options(contrasts = c("contr.treatment", "contr.poly"))
```

### Direct Evaluative ratings

**(1) Analysis of Difference scores:**

**H1** Wider generalization when the category size is large, in comparison to the small category size. This translates into a significant category size x stimulus type interaction. We expect this for both evaluative ratings and the AMP.


**ANOVA**

```{r, echo = FALSE, include = TRUE}

##ANOVA

anovaDiff <- aov_car(diff ~ condition*type_specific + Error (subject / type_specific), directDiff)
anovaDiff
eta_sq(anovaDiff, partial = TRUE)


```



**mixed effect models**

Diff score per individual, type and category e.g. [VP1 CS cat1 pos] - [VP1 CS cat2 neg]
condition (-0.5 = one, 0.5 = many), type (-0.5 = CS, 0.5 = GS)

Model with random intercepts for participants:
lmer(diff ~ condition* type + (1|subject))

*significant interaction: H1*

```{r, echo = TRUE, include = TRUE}
## specify models
lmer1Diff <- lmer(diff ~ condition_effect*type_effect 
                  + (1|subject), 
                  directDiff, REML = FALSE)

lmer2Diff <- lmer(diff ~ condition_effect*type_effect 
                  + (type_effect|subject), 
                  directDiff, REML = FALSE)

anova(lmer1Diff, lmer2Diff)
```

The difference in deviance between Model 1 and Model 2 is not significant X²(2, 1594) = 2.48, p = .068 This indicates that including a random slope effect does not contribute to a better fitting model than a mere random intercept effect.

```{r, echo = TRUE, include = TRUE}
summary(lmer1Diff, corr = FALSE)
#choose model1

```

Parameter Interpretation: lmer1Diff

**Random Intercept subjects = 39.86** -> variation of intercepts across subjects (goes beyond the fixed effect of stimulus type -> there are substantial interindividual differences in the average evaluative ratings of participants)

**Intercept = 50.114** -> Grand mean (on average, difference scores were 50.114 points)

**Fixed Effect Condition = 10.706** -> main effect condition: The mean difference between conditions in difference scores was 10.706: 10.706 points higher in the "many" condition than in the "one" condition.

**Fixed Effect Type = -28.845** -> main effect type: the mean difference between stimulus types in difference scores was -28.845: 28.845 points lower in for "GSs" than for "CSs".

**Interaction TypexCondition = 22.91** -> interaction effect condition*type: the difference between "one" and "many" for CSs and "one" and "many" for GSs was 22.91 in total, indicating that the effect of condition was qualified by the type of stimulus.

Simple slopes:
lmer (diff ~ type (effect coded) + condition (effect coded): type (dummy coded) + (1|subject))

```{r, echo = TRUE, include = TRUE}
#model1: analyze simple slopes
lmer1_1Diff <- lmer(diff ~ type_effect + condition_effect:type_specific
                    + (1|subject),
                    directDiff, REML = FALSE)
summary(lmer1_1Diff, corr = FALSE)
```

Parameter Interpretation: lmer1_1Diff

**Interaction TypeCS x Condition = -0.75** -> Effect of condition for CSs is -0.75 (on average, the difference scores are 0.75 points lower in the "many" condition than in the "one" condition, when looking at CSs)

**Interaction TypeGS x Condition = 22.16** -> Effect of condition for GSs is 22.16 (on average, the difference scores are 22.16 points higher in the "many" condition than in the "one" condition, when looking at GSs)
-> this is the finding that we are looking for


```{r, echo = FALSE, include = TRUE}
#plot model1
boxplot2 <- ggplot(directDiff, aes (x = type_specific, y = diff, color = condition)) +
  geom_boxplot() +
  ggtitle("Direct Evaluative Ratings\n") + 
  scale_color_brewer(palette = "Set2") +
  scale_x_discrete(name = "\n Type") +
  scale_y_continuous (name = "Difference Scores\n") + 
  theme_classic() +
  labs(color = "Condition") +
  theme(plot.title = element_text (hjust = 0.5, face = "bold", size = 14),
        text = element_text(size=14))
boxplot2

## use two-way interaction for power analysis
```
 
 **(2) Include Valence as a factor, use raw evaluative rating scores as DV**
 
 **ANOVA**

```{r, echo = FALSE, include = TRUE}

##ANOVA

anovaVal <- aov_car(response ~ condition*type_specific*val + Error (subject / type_specific*val), direct)
anovaVal
eta_sq(anovaVal, partial = TRUE)


```

**mixed models**

condition (-0.5 = one, 0.5 = many), type (-0.5 = CS, 0.5 = GS), val (-0.5 = neg, 0.5 = pos)

Model with random intercepts for participants:
lmer(ratings ~ condition* type* val + (1|subject))

```{r, echo = TRUE, include = TRUE}
#analysis 2: with valence as a factor

#random intercepts
lmer1 <- lmer(response ~ val_effect*condition_effect*type_effect 
              + (1|subject), 
              direct, REML = FALSE)

#random slopes
lmer2 <- lmer(response ~ val_effect*condition_effect*type_effect 
              + (val_effect*type_effect|subject), 
              direct, REML = FALSE)
anova(lmer1, lmer2)
summary(lmer2, corr = FALSE)
#choose model2

```


(1) simple slopes:

Model with random intercepts and slopes for participants, testing if the difference between pos and neg (EC effect) is significant for each combination of type x category size:

lmer(diff ~ condition (effect coded) * type_specific (effect coded) + val (effect coded)* type (dummy coded) * condition(dummy coded) +  (type(effect coded) * val(effect coded)|subject))

```{r, echo = TRUE, include = TRUE}
#model2
lmer1_2 <- lmer(response ~ condition_effect*type_effect + val_effect:condition:type_specific
                + (val_effect*type_effect|subject),
                direct, REML = FALSE)
summary(lmer1_2, corr = FALSE)
```


```{r, echo = FALSE, include = TRUE}
#plot model2

boxplot2 <- ggplot(direct, aes (x = type_specific, y = response, color = val)) +
  facet_grid(. ~ condition) +
  geom_boxplot() +
  ggtitle("Direct Evaluative Ratings\n") + 
  scale_color_brewer(palette = "Set2") +
  scale_x_discrete(name = "\n Type") +
  scale_y_continuous (name = "Evaluative Ratings\n") + 
  theme_classic() +
  labs(color = "Condition") +
  theme(plot.title = element_text (hjust = 0.5, face = "bold", size = 14),
        text = element_text(size=14))
boxplot2
```

(2) simple slopes:

Model with random intercepts and slopes for participants, testing the difference for category sizes for each combination of valence and stimulus type:

lmer(diff ~ type (effect coded) * val (effect coded) + condition (effect coded)* type (dummy coded) * val(dummy coded) +  (type(effect coded) * val(effect coded)|subject))

```{r, echo = TRUE, include = TRUE}
#model3
lmer1_3 <- lmer(response ~ val_effect*type_effect + condition_effect:val:type_specific
                + (val_effect*type_effect|subject),
                direct, REML = FALSE)
summary(lmer1_3, corr = FALSE)
```


```{r, echo = FALSE, include = TRUE}
#plot model3

boxplot3 <- ggplot(direct, aes (x = type_specific, y = response, color = condition)) +
  facet_grid(. ~ val) +
  geom_boxplot() +
  ggtitle("Direct Evaluative Ratings\n") + 
  scale_color_brewer(palette = "Set2") +
  scale_x_discrete(name = "\n Type") +
  scale_y_continuous (name = "Evaluative Ratings\n") + 
  theme_classic() +
  labs(color = "Condition") +
  theme(plot.title = element_text (hjust = 0.5, face = "bold", size = 14),
        text = element_text(size=14))
boxplot3
```


```{r, echo = FALSE, include = FALSE}
# AMP ---------------------------------------------------------------------

knitr::opts_knit$set(root.dir = DRM)


indirect <- read.csv2("indirect.csv", header = TRUE)

#delete columns we don't need
indirect$X <- NULL
indirect$type <- NULL
str(indirect)

as_factor <- c("subject", "val", "condition", "measure", "type_specific", "category", "cs_selected", "target")

for (factor in as_factor){
  indirect[, factor] <- as.factor(indirect[,factor])
}

indirect$type_specific <- factor(indirect$type_specific, levels = c("CS", "GS same", "GS different", "Feature", "Group"))


## randomly select 1 CS for many_one:
new_one <- indirect[indirect$condition == "one_one",]
new_many <- indirect[indirect$condition == "many_one",]

#remove the original CS evaluations
new_many <- new_many[!new_many$type_specific == "CS",]
new_indirect <- rbind(new_one, new_many)

for (subject in unique(indirect$subject)){
  if (indirect$condition[indirect$subject == subject] == "many_one"){
    for (cat in 1:4){
      temp <- indirect[indirect$subject == subject & indirect$type_specific == "CS" & indirect$category == cat,]
      select <- temp[1,]
      #concat only 1 CS rating per participant
      new_indirect <- rbind(new_indirect, select)
    }
  }
}
head(new_indirect)

temp <- new_indirect

# order data
temp <- temp[order(temp$subject, temp$val, temp$type_specific),]

# omit information we don't need
temp <- temp[!temp$type_specific =="GS different", ]
temp <- temp[!temp$type_specific == "Feature",]

## rename many_one to many and one_one to one
temp$condition <- factor(temp$condition, labels = c("one", "many"), levels = c("one_one", "many_one"))

##categorical variable: generalization as discrete
temp$type_specific <- factor(temp$type_specific, labels = c("CS", "GS"), levels = c("CS", "GS same"))
head(temp)

## effect code variables
#condition
temp$condition_effect <- 0
for (line in 1:dim(temp)[1]){
  if (temp$condition[line] == "one"){
    temp$condition_effect[line] <- -0.5
  } else {
    temp$condition_effect[line] <- 0.5
  }
}
temp$condition_effect

#valence
temp$val_effect <- 0
for (line in 1:dim(temp)[1]){
  if (temp$val[line] == "neg"){
    temp$val_effect[line] <- -0.5
  } else {
    temp$val_effect[line] <- 0.5
  }
}
temp$condition_effect
str(temp)

#type
temp$type_effect <- 0
for (line in 1:dim(temp)[1]){
  if (temp$type_specific[line] == "CS"){
    temp$type_effect[line] <- -0.5
  } else {
    temp$type_effect[line] <- 0.5
  }
}
temp$type_specific
str(temp)

#set default to dummy coding
options(contrasts = c("contr.treatment", "contr.poly"))

### specify models
indirect <- temp
indirect$response <- as.numeric(indirect$response)
indirect <- indirect[order(indirect$subject, indirect$val, indirect$type_specific, indirect$category),]

indirectProp <- aggregate(response ~ subject + val_effect + val + type_effect + type_specific
                          + condition + condition_effect, indirect, sum)
indirectProp$length <- aggregate(response ~ subject + val_effect + val + type_effect + type_specific
                                 + condition + condition_effect, indirect, length)[[8]]
indirectProp$prop <- indirectProp$response/indirectProp$length
hist(indirectProp$prop)
head(indirectProp)

##### analysis 1: with difference scores
indirectNeg <- indirectProp[indirectProp$val == "neg",]
indirectPos <- indirectProp$prop[indirectProp$val == "pos"]

indirectDiff <- cbind(indirectNeg, indirectPos)
names(indirectDiff)[names(indirectDiff) == "prop"] <- "propNeg"
names(indirectDiff)[names(indirectDiff) == "indirectPos"] <- "propPos"

indirectDiff$diff <- indirectDiff$propPos - indirectDiff$propNeg
indirectDiff[indirectDiff$subject == "02a80kdxm7",]

aggregate(diff ~ condition*type_specific, indirectDiff, mean)
aggregate(diff ~ condition*type_specific, indirectDiff, se)
```

### AMP

**(1) Analysis of Difference scores:**

**H1** Wider generalization when the category size is large, in comparison to the small category size. This translates into a significant category size x stimulus type interaction with a positive parameter estimate. We expect this for both evaluative ratings and the AMP.


Difference scores: per participant and stimulus type: [proportion of "angenehm" responses for +] - [proportion of "angenehm" responeses for -] 

condition (-0.5 = one, 0.5 = many), type (-0.5 = CS, 0.5 = GS)

Model with random intercepts for participants:
lmer(diff ~ condition* type + (1|subject))

*signifikant interaction: H1*


```{r, echo = TRUE, include = TRUE}
#model specification
lmer1Diff <- lmer(diff ~ condition_effect*type_effect + (1|subject), indirectDiff, REML = FALSE)

#lmer2Diff <- lmer(diff ~ condition_effect*type_effect + (type_effect|subject), indirectDiff, REML=FALSE)
#model 2 not specifiable due to missing observations

#anova(lmer1Diff, lmer2Diff)

summary(lmer1Diff, corr = FALSE)
```

Simple slopes:
lmer (diff ~ type (effect coded) + condition (effect coded): type (dummy coded) + (1|subject))


```{r, echo = TRUE, include = TRUE}
#simple slopes
lmer1Diff_1 <- lmer(diff ~ type_effect + type_specific:condition_effect + (1|subject), indirectDiff, REML = FALSE)
summary(lmer1Diff_1, corr = FALSE)
```


```{r, echo = FALSE, include = TRUE}
#plot1
indirect_plot1 <- aggregate(diff ~ condition*type_specific, indirectDiff, mean)
indirect_plot1$se <- aggregate(diff ~ condition*type_specific, indirectDiff, se) [[3]]

barplot1 <- ggplot(indirect_plot1, aes (y = diff, x = type_specific, fill = condition)) +
  geom_col(position = position_dodge()) +
  geom_errorbar(aes(ymin= diff - se, ymax= diff + se), width=.2,
                position=position_dodge(.9)) +
  ggtitle("AMP\n") + 
  scale_color_brewer(palette = "Set2") +
  scale_x_discrete(name = "\n Type") +
  scale_y_continuous (name = "Difference Scores\n") + 
  theme_classic() +
  labs(fill = "Condition") +
  theme(plot.title = element_text (hjust = 0.5, face = "bold", size = 14),
        text = element_text(size=14))
barplot1
```



 **(2) Include Valence as a factor, use prop "angenehm" as DV**

response: 1 = "angenehm", 0 = "unangenehm"
condition (-0.5 = one, 0.5 = many), type (-0.5 = CS, 0.5 = GS), val (-0.5 = neg, 0.5 = pos)

Model with random intercepts for participants and targets:
glmer(response ~ condition* type* val + (1|subject) + (1|target))

```{r, echo = TRUE, include = TRUE}
####analysis 2: with valence as additional variable

#random intercept for participants
glmer1 <- glmer(response ~ val_effect*condition_effect*type_effect 
                + (1|subject), 
                indirect, binomial)

#random intercept for targets
glmer2 <- glmer(response ~ val_effect*condition_effect*type_effect 
                + (1|subject) + (1|target), 
                indirect, binomial)

#random slopes for participants (fails to converge)
'glmer3 <- glmer(response ~ val_effect*condition_effect*type_effect 
                + (val_effect*type_effect|subject) + (1|target), 
                indirect, binomial)'

#random slopes for targets (converges, but does not lead to better model fit)
'glmer4 <- glmer(response ~ val_effect*condition_effect*type_effect 
              + (val_effect*type_effect|subject) + (val_effect*type_effect|target), 
              indirect, binomial)'
anova(glmer1, glmer2)
#model choice: glmer2

summary(glmer2, corr = FALSE)

```

simple slopes:

Model with random intercepts for participants and random intercepts for targets:
glmer(response ~ type (effect coded) * val (effect coded) + condition (effect coded)* type (dummy coded) *val(dummy coded) +  (1|subject) + (1|target))


```{r, echo = TRUE, include = TRUE}
#analyze simple slopes (even though three-way-interaction is not significant)
glmer2_2 <- glmer(response ~ val_effect*type_effect + val:type_specific:condition_effect
                 + (1|subject) + (1|target), indirect, binomial)
summary(glmer2_2, corr = FALSE)
#significant three-way interaction
```


```{r, echo = FALSE, include = TRUE}
#plot model1
indirect_plot2 <- aggregate(prop ~ condition + val + type_specific, indirectProp, mean)
indirect_plot2$se <- aggregate(prop ~ condition + val + type_specific, indirectProp, se)[[4]]

barplot2 <- ggplot(indirect_plot2, aes (y = prop, x = type_specific, fill = condition)) +
  facet_grid(. ~ val) +
  geom_col(position = position_dodge()) +
  geom_errorbar(aes(ymin= prop - se, ymax= prop + se), width=.2,
                position=position_dodge(.9)) +
  geom_hline(yintercept = 0.5, col = "black") +
  ggtitle("Direct Evaluative Ratings\n") + 
  scale_color_brewer(palette = "Set2") +
  scale_x_discrete(name = "\n Valence") +
  scale_y_continuous (name = "Proportion pleasant\n") + 
  theme_classic() +
  labs(fill = "Condition") +
  theme(plot.title = element_text (hjust = 0.5, face = "bold", size = 14),
        text = element_text(size=14))
barplot2
```


```{r, echo = FALSE, include = FALSE}
# recognition memory ------------------------------------------------------
setwd(DRM)

memory <- read.csv2("memory1.csv", header = TRUE)
str(memory)

#delete columns we don't need
memory$X <- NULL
memory$memoryCorrect <- NULL
memory$trial_index <- NULL
memory$task <- NULL
memory$rt <- NULL

#rename condition
names(memory)[names(memory) == "condition1"] <- "condition"

#delete trials with timeout
memory <- memory[!memory$timeout == "true",]
str(memory)
#as factor
as_factor <- c("subject", "condition", "type", "category", "cs_selected")

for (factor in as_factor){
  memory[, factor] <- as.factor(memory[,factor])
}

temp <- memory

# omit information we don't need
temp <- temp[!temp$type =="CSpred", ]
temp <- temp[!temp$type =="CSnonpred", ]
temp <- temp[!temp$type =="GSnew", ]
temp <- temp[!temp$type == "distractor",]
temp <- temp[!temp$condition == "many_fill",]

# order data
temp <- temp[order(temp$subject, temp$type),]

## rename many_one to many and one_one to one
temp$condition <- factor(temp$condition, labels = c("one", "many"), levels = c("one_one", "many_one"))

##categorical variable: generalization as discrete
temp$type <- factor(temp$type, labels = c("CS", "GS"), levels = c("CS", "GSold"))
head(temp)

## effect code variables
#condition, one = 0.5
temp$condition_effect <- 0
for (line in 1:dim(temp)[1]){
  if (temp$condition[line] == "one"){
    temp$condition_effect[line] <- -0.5
  } else {
    temp$condition_effect[line] <- 0.5
  }
}
temp$condition_effect


#type, GS = 0.5
temp$type_effect <- 0
for (line in 1:dim(temp)[1]){
  if (temp$type[line] == "CS"){
    temp$type_effect[line] <- -0.5
  } else  {
    temp$type_effect[line] <- 0.5
  } 
}
temp$type_effect
str(temp)

memory <- temp
memory$memoryResp <- as.numeric(memory$memoryResp)
memory <- memory[order(memory$subject, memory$type, memory$category),]
str(memory)

#for plotting
memoryProp <- aggregate(memoryResp ~ subject + type + condition, memory, sum)
memoryProp$length <- aggregate(memoryResp ~ subject + type + condition, memory, length)[[4]]
memoryProp$prop <- memoryProp$memoryResp/memoryProp$length
hist(memoryProp$prop)
head(memoryProp)

##### analysis 1: glmers
#set default to dummy coding
options(contrasts = c("contr.treatment", "contr.poly"))

```

**(1) Analysis of Difference scores:**

**H2**: Higher false memory rates when the category size is large, in comparison to the small category size. This translates into a significant category size x stimulus type interaction. We expect this for the recognition memory measure.


for memory responses (1 = "old", 0 = "new")
condition (-0.5 = one, 0.5 = many), type (-0.5 = CS, 0.5 = GS)

Model with random intercepts for participants and stimulus:
glmer(memoryResp ~ condition* type + (1|subject) + (1|stimulus))

*signifikant interaction: H2*



```{r, echo = TRUE, include = TRUE}
#random intercept and slope for participants
glmer1 <- glmer(memoryResp ~ condition_effect * type_effect
                + (1|subject), 
                memory, binomial)

#random intercept and slope for stimuli for participants
glmer2 <- glmer(memoryResp ~ condition_effect*type_effect 
                + (1|subject) + (1|cs_selected), 
                memory, binomial)

#random intercept and slope for stimuli for participants
glmer3 <- glmer(memoryResp ~ condition_effect*type_effect 
                + (type_effect|subject) + (1|cs_selected), 
                memory, binomial)

#random intercept and slope for targets (does not converge)
glmer4 <- glmer(memoryResp ~ condition_effect*type_effect 
                + (type_effect|subject) + (type_effect|cs_selected), 
                memory, binomial)

anova(glmer1, glmer2, glmer3, glmer4)

#model choice: glmer2
summary(glmer2, corr = FALSE)
```

simple slopes:

Model with random intercepts for participants and random intercepts for targets:
glmer(memoryResp ~ type (effect coded) + condition (effect coded)* type (dummy coded) +  (1|subject) + (1|target))


```{r, echo = TRUE, include = TRUE}
#analyze simple slopes (even though three-way-interaction is not significant)
glmer2_2 <- glmer(memoryResp ~ type_effect + type:condition_effect
                  + (1|subject) + (1|cs_selected), memory, binomial)
summary(glmer2_2, corr = FALSE)
```


```{r, echo = FALSE, include = TRUE}
#plot model1
memory_plot2 <- aggregate(prop ~ condition + type, memoryProp, mean)
memory_plot2$se <- aggregate(prop ~ condition + type, memoryProp, se)[[3]]

barplot1 <- ggplot(memory_plot2, aes (y = prop, x = type, fill = condition)) +
  geom_col(position = position_dodge()) +
  geom_errorbar(aes(ymin= prop - se, ymax= prop + se), width=.2,
                position=position_dodge(.9)) +
  ggtitle("DRM\n") + 
  scale_color_brewer(palette = "Set2") +
  scale_x_discrete(name = "\n Type") +
  scale_y_continuous (name = "Proportion 'old'\n") + 
  theme_classic() +
  labs(fill = "Condition") +
  theme(plot.title = element_text (hjust = 0.5, face = "bold", size = 14),
        text = element_text(size=14))
barplot1

```

